%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}

\usepackage[top=0.8cm, bottom=0.2cm, left=1cm, right=1cm]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}


%for social icons
\usepackage{fontawesome5}

% job listing environments
\newenvironment{jobshort}[3]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \textit{#2} &  #3 \\[3pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[3]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \textit{#2} &  #3 \\[3pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Sameer Tripathi} \\[8pt]
\href{tel:+919151426933}{\ +91 9151426933} \ $|$ \
\href{mailto:sameertrip123@gmail.com}{\ sameertrip123@gmail.com} \ $|$ \
\href{https://linkedin.com/in/sameertri039}{\ LinkedIn} \ $|$ \ 
\href{https://github.com/sameertrip123}{\ GitHub} \ $|$ \ 
\href{https://sameertrip123.github.io/portfolio/}{\ Portfolio}  \ $|$ \ 
\href{https://leetcode.com/u/sameertri039/}{\ LeetCode} \ $|$ \
\href{https://www.geeksforgeeks.org/user/sameertri039/}{\ GeeksforGeeks}  \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\vspace{-4pt}
\begin{joblong}{Indian Institure of Information Technology (IIIT Kurnool)}{B. Tech in Computer Science}{Dec 2020 - May 2024}
    \item Courses: Data Structures, Algorithms, Object Oriented Programming, DBMS, Operating Systems, Distributed System
\end{joblong}
\vspace{-16pt}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------
\section{Experience}
\vspace{-4pt}
\begin{joblong}{Recruit CRM}{Software Engineer Intern}{Oct 2023 - Present}
    \item Revamped the candidates module, migrating the tech stack from PHP to Java, Spring Boot, Microservices and SOA, yielding a performance boost of 29.73\%.
    \item Conducted POCs for 14 different existing endpoints, contributed to high-level and low-level design, developed new endpoints, and meticulously documented the entire process.
    \item Wrote unit tests for the new endpoints using JUnit and Mockito, ensuring 100\% code coverage.
    \item Exposure: Java, Spring Boot, MySQL, AWS(EC2, S3), JUnit, Mockito, JIRA, Confluence, CI/CD, Sonar, Agile, Scrum
\end{joblong}

% \begin{joblong}{DoSelect - {\footnotesize \textit{\textbf{(Naukri.com)}}}}{Problem Setter}{Jan 2024 - Present}
%     \item Collaborated with 7 other team members to create coding problems for hiring assessments and online tests.
%     \item Improved problem clarity for 20+ problems, added test cases and code stubs for new problems, wrote editorials for
%     problems and their solutions for thorough explanation.
% \end{joblong}

% \begin{joblong}{Outscal}{Intern - C++}{Aug 2023 - Present}
%     \item Reviewed C++, Data Structures, Object-Oriented Programming (OOPS) assignments within 24-hour, addressing
%     queries promptly and ensuring the satisfaction of over 20+ students.
%     \item Conducted code reviews, provided actionable feedback that accelerated student’s progress by 10\% within 2 months.
% \end{joblong}

\begin{joblong}{Samsung R\&D}{Prism Research Intern}{Jan 2023 - Mar 2023}
    \item Designed an IoT service that connects to the best available access point for optimal speed and throughput.
    \item Leveraged QoS parameters to achieve sub-300 millisecond latency, enhancing overall user experience.
\end{joblong}
\vspace{-5pt}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\vspace{-4pt}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Langauges &  \normalsize{C, C++, Java, Golang, SQL}\\
Web Development & \normalsize{HTML, CSS, JavaScript, Vue.js, Tailwind CSS}\\
Frameworks &  \normalsize{Laravel, Spring Boot, Spring Data JPA, Hiberate}\\
Database & \normalsize{MySQL, MongoDB, Redis, CI/CD, JUnit, Mockito, Maven, SonarQube}\\
Familiar With & \normalsize{AWS (S3, EC2, Aurora), Kafka, Jenkins, Docker}\\
Developer Tools & \normalsize{Git, JIRA, Confluence, Postman, VS Code, IntelliJ IDEA}\\
\end{tabularx}



%----------------------------------------------------------------------------------------
  
\section{Projects}
\vspace{-4pt}
\begin{jobshort}{Task Scheduler}{PHP, Laravel, Vue.js, MySQL, Tailwind CSS}{\href{https://github.com/sagnik6969/task_scheduler_frontend}{\raisebox{-0.05\height}\faGithub\ GitHub}}
    A task scheduler application for managers to create, organize, and monitor tasks. Implemented email verification and
notifications for timely updates.
\end{jobshort}

\begin{jobshort}{Distributed Cache}{Golang}{}
    Implemented a distributed cache system for efficient data storage and retrieval across network nodes.
\end{jobshort}

\begin{jobshort}{File Hider}{Java, JDBC, SMTP}{}
    An application that allows users to hide and unhide their files in a secure wallet. Added 2 factor authentication using OTP
    on their registered mail.
\end{jobshort}

\begin{jobshort}{URL Shortener}{Golang, Redis, Fiber}{\href{https://github.com/sameertrip123/url-shortener}{\raisebox{-0.05\height}\faGithub\ GitHub}}
    A high performant URL shortener that converts long URLs to a short URL. Utilized Redis for URL mapping. Simplified
    URL validation and integrated rate limiting to prevent abuse by malicious users.
\end{jobshort}



\section{Achievements}
\vspace{-4pt}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt,label=--]
    \item Ranked 5577 and 3532 globally in Meta Hacker Cup 2023 Rounds 1 and 2. \href{https://www.facebook.com/codingcompetitions/hacker-cup/2023/certificate/2037824066570201}{Certificate}
    \item Secured a global rank of 4614 out of 10K+ participants in Google Kick Start 2022 Round F. \href{https://drive.google.com/file/d/1yJX57VkI7LnC7MsX_Wz_063uCRgkH8W3/view}{Certificate}
    \item Achieved global rank 4011 out of 28991 participants in Scalar CodeX 2.0 coding contest. \href{https://moonshot.scaler.com/s/sl/p3M5EL9en3}{Certificate}
    \item Secured global rank 3109 out of 20K+ participants in LeetCode Weekly Contest 320. \href{https://leetcode.com/u/sameertri039/}{Profile}
\end{itemize}


\section{Freelancing}
\vspace{-4pt}
\begin{joblong}{DoSelect - {\footnotesize \textit{\textbf{(Naukri.com)}}}}{Problem Setter}{Jan 2024 - Present}
    \item Collaborated with 7 other team members to create coding problems for hiring assessments and online tests.
    \item Improved problem clarity for 20+ problems, added test cases and code stubs for new problems, wrote editorials for
    problems and their solutions for thorough explanation.
\end{joblong}

\begin{joblong}{Outscal}{Intern - C++}{Aug 2023 - Present}
    \item Reviewed C++, Data Structures, Object-Oriented Programming (OOPS) assignments within 24-hour, addressing
    queries promptly and ensuring the satisfaction of over 20+ students.
    \item Conducted code reviews, provided actionable feedback that accelerated student’s progress by 10\% within 2 months.
\end{joblong}

\end{document}